%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Doctor of Philosophy (Ph.D.) - ``Large-Scale Relationship Extraction"} % Institution
	{Instituto Superior Técnico, University Lisbon} % Degree
    {Lisbon, Portugal} % Location
    {Feb. 2011 - Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Researched different methods to perform semantic relationship extraction between named-entities and proposed a classifier based on the idea of nearest neighbour and leveraging min-hash and locality sensitive hashing for efficient similarity search.}
		\item {To obtain training data for the classifier I proposed a bootstrapping technique relying on distributional word representations which was awarded an {\it Honorable Mention for Best Short Paper} at \textbf{EMNLP'15}.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Master of Science (M.Sc.) - ``Geographic Text Mining"} % Institution
	{Faculty of Sciences, University of Lisbon} % Degree
    {Lisbon, Portugal} % Location
    {Sep. 2007 - Jul. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed a geographic information extraction system based on Conditional Random Fields and a geographic ontology, to generate geographic summaries. The summary lists all the geographic entities found in a document mapped to unique concepts in the geographic ontology.}
		\item {The system was then applied to a crawl of the Portuguese Web (25GB raw text) using a Hadoop cluster, generating summaries for hundreds of thousands of documents.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Bachelor's in Informatics Engineering} % Institution
	{Faculty of Sciences, University of Lisbon | Universität Karlsruhe, Germany} % Degree
    {Lisbon, Portugal} % Location
    {Sep. 2003 - Jul. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {2005-2006, Karlsruhe Universität (TH), Germany - 2 semesters as an exchange student}
		\item {2004 November - 2005 July - IT support (part-time) - troubleshooting network infrastructure and preventative maintenance.}
		\item {2003 November - 2004 March - Sys Admin (part-time) - administration and configuration of the IT department network and services.}
      \end{cvitems}
    }

% Troubleshooting network infrastructure, preventative maintenance, helping and educating new users \\
% Administration and configuration of networking software and services, e.g.: SAMBA, IMAP, Apache HTTP Server, IPTables, crontab scheduling, backups;       
	
	

%---------------------------------------------------------
\end{cventries}
