%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Senior Data Scientist} % Job title
    {Veeva Systems - Senior Data Scientist} % Organization
    {Berlin, Germany} % Location
    {Mar 2023 - Present} % Date(s)
	{
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed within the Veeva Link product a model using PySpark MLlib to categorize life-science organisations using a 2 million-sample multilingual dataset and open data resources, reducing curator workload by 10\%. Additionally, I enhanced the researcher-to-activity linking model with pre-trained static embeddings in a 3.2 billion-sample annotated dataset, resulting in a 2\% model performance improvement.}
		\item {Implemented Python development best practices (tests, linting, PEP 8, type hints) within a CI pipeline and mentored junior data scientists in applying the same practices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead NLP Engineer} % Job title
    {TripActions/Navan (acquired Comtravo GmbH)} % Organization
    {Berlin, Germany} % Location
    {May 2022 - Feb 2023} % Date(s)
	{
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Joined through the acquisition of Comtravo by TripActions/Navan and my team was tasked with developing a chatbot's NLP/NLU component to automate customer support.}
		\item {We incorporated some of the previously developed components from the email channel into the new chat channel.}
		\item {Defined an intent and entities schema, set up the infrastructure for annotation based on argilla.io open source annotation tool and onboarded annotators to the annotation task.}
		\item {Defined and implemented an entropy-based active-learning strategy to select samples to annotate.}
		\item {Fine-tuned, evaluated, performed threshold tuning and deployed different classifiers based on pre-trained Transformer architectures.}
      \end{cvitems}
    }


%---------------------------------------------------------

\cventry
    {Lead NLP Engineer} 
    {Comtravo GmbH} 
    {Berlin, Germany} 
    {May 2021 - Feb 2022}
    {
      \begin{cvitems} 
		  \item {Led a team of 3 developers guiding them in technical decisions and supervised system changes, and also managed the 4 annotators.}
		  \item {Managed bi-weekly sprint planning and execution, coordinating development tasks based on system performance and feature requests.}
		  \item {Defined quantifiable measures in collaboration with the Data Engineering team, resulting in performance reports and monitoring dashboards.}
		  \item {Supervised the data annotation by ensuring annotation quality and consistency across the whole corpora.}
		  \item {Continued to maintain an active role in software development: implementing new features, maintenance, refactoring and code reviews.}
        \end{cvitems}
 	}


  \cventry
    {Senior NLP Engineer}
    {} % Organization EMPTY
    {} % Location EMPTY
    {Aug 2017 - Apr 2021} % Date(s)
    {
      \begin{cvitems}
		\item {Collaborated from it's inception in building an automation system to support travel agents in creating trip itineraries offers from incoming emails with business travel requests, working together with the team in multiple tasks.}
		\item {Developed several supervised models for text classification and sequence tagging using different architectures.}
		\item {Built Knowledge Bases containing worldwide descriptions of airport and train stations based on open resources and in-house operational data.}
		\item {Developed entity-linking approaches to map entities (e.g: airports, train stations, hotels) into unique identifiers in Knowledge Bases.}
		\item {Developed a ranking and selection of trip itineraries offers based on the Pareto Efficiency algorithm.}
		\item {Developed several modularised Python components with type-annotations, linting and test coverage of 95\%.}
		\item {The automation system generating travel itineraries from customer emails reduced by 30\% the workload of travel-agents.}
        \end{cvitems}
 	}

%------------------------------------------------------------------------------------------------------------


\begin{comment}
  \cventry
    {Lead NLP Engineer} % Job title
    {Comtravo GmbH} % Organization
    {Berlin, Germany} % Location
    {Aug 2017 - Apr 2022} % Date(s)
	{
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Joined as an NLP Engineer in August 2017, was promoted to Senior NLP Engineer in July 2019, and in June 2021 to Lead NLP Engineer.}
        \item {Led a team of 3 developers + 4 annotators, working on the system that automatically answers incoming email travel requests and assists travel agents in handling them. Coordinating development tasks based on system performance and feature requests.}
        \item {Trained, evaluated and improved different models for text classification and fine-grained NER, increasing the performance of identifying specific booking requests and performing information extraction to automatically fulfil booking requests.}
		\item {Developed algorithms to map input text into unique Knowledge Base identifiers, e.g: airports, train stations, hotels, geographic locations.}		
      \end{cvitems}
    }
\end{comment}


%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {HelloFresh SE} % Organization
    {Berlin, Germany} % Location
    {Jan 2016 - Jun 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was part of the initial Data Engineering team tasked with transitioning from crontab-based processes to an ETL platform.}
        \item {Developed the initial prototype for ETL management using Airflow, which evolved into the production data pipeline management system.}
		\item {Conceptualised and developed multiple ETL processes with the PySpark ecosystem and orchestrated by Airflow.}
        \item {Developed a classifier to identify customer feedback review mentioning issues with the ordered meal kits.}
      \end{cvitems}
    }
	
%---------------------------------------------------------
  \cventry
    {Researcher and Developer: \href{http://arquivo.pt/wayback/20151118124735/http://dmir.inesc-id.pt/project/Reaction}{REACTION - Computational Journalism}} % Job title
    {INESC-ID Research \& Development Institute} % Organization % - \href{http://arquivo.pt/wayback/20151118124735/http://dmir.inesc-id.pt/project/Reaction}{REACTION - Computational Journalism
    {Lisbon, Portugal} % Location
    {Jun 2011 - Apr 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Explored and implemented methods for entity-relationship extraction, based on: hand-built patterns, supervised linear classifiers with linguistic features and semi-supervised methods based on seed relationships and large amounts of unannotated text.}
		\item {Developed an entity-linking approach associating personalities in news articles with Wikipedia using textual similarities and its graph structure.}
        \item {Built a graph based on topic models extracted from news articles and person co-occurrences, allowing to explore topics connecting persons.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Researcher and Developer: \href{https://arquivo.pt/wayback/20181014115718/http://xldb.di.fc.ul.pt/wiki/Grease}{GREASE - Geographic Reasoning for Search Engines}} % Job title
    {LaSIGE - Department of Informatics Research Unit } % Organization %
    {Lisbon, Portugal} % Location
    {Sep 2008 - Oct 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a method to disambiguate toponyms based on textual context, information content and topological similarity measures.}
        \item {Built an alignment method between two geo-ontologies resulting in a single linked-data ontology, allowing the inclusion of features from both ontologies in SPARQL queries.}
		%\item {Published scientific articles with the outcome of these tasks.}
		% \item {Identified, based on n-grams, the language of each page of a 10 million pages web crawl and used this data to identify top Portuguese names overlapping with toponyms}. 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Nokia-Siemens Networks} % Organization % - \href{https://arquivo.pt/wayback/20181014115718/http://xldb.di.fc.ul.pt/wiki/Grease}{Geographic Reasoning for Search Engines}
    {Lisbon, Portugal} % Location
    {Oct 2007 - Jul 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {An 80\% position while I took the remaining 20\% to finish my M.Sc. curriculum component.}
        \item {Developed data collection modules for a GSM monitoring system using Java, CORBA Architecture and Oracle RDBMS.}
      \end{cvitems}
    }

\end{cventries}
