\cvsection{Personal Projects}


\begin{cventries}
  \cventry
    {Politiquices.PT - https://www.politiquices.pt} % Degree
    {Analysis of support and opposition political relationships} % Institution
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {A website to explore political interactions of support and opposition based on news articles.}
		\item {Awarded the \textbf{2nd place on the "Arquivo.pt Awards 2021"} organised by the Portuguese Web Archive.}
		\item {Using an API, I crawled news headlines mentioning politicians and annotated a sample in order to build supervised models to detect relationships between politicians and link them to Wikidata.}
		\item {Applied the trained models to crawled data and generated a semantic graph connecting politicians through a support or opposition relationship sustained by news articles.}
		\item {Using a SPARQL endpoint it's possible to issue queries like: \textit{Which politicians affiliated with party X opposed/supported politicians from party Y?}}
		\item {The project gained the interest of journalists, political scientists and social humanities researchers.}
      \end{cvitems}
    }
 \cventry
   {https://pypi.org/project/breds/} % Degree
   {BREDS - Bootstrapping Semantic Relationships with Distributional Semantics} % Institution
   {} % Location
   {} % Date(s)
   {
     \begin{cvitems} % Description(s) bullet points
     	\item {An open-source project to extract named-entity relationships based on work done during my PhD thesis.}
		\item {Still active in GitHub with a few contributions from other developers.}
     \end{cvitems}
   }
 \cventry
   {https://pypi.org/project/nervaluate/} % Degree
   {nervaluate - NER evaluation considering partial entity matching.} % Institution
   {} % Location
   {} % Date(s)
   {
     \begin{cvitems} % Description(s) bullet points
     	\item {An open-source project to evaluate named-entity recognition systems considering partial entity matching.}
      \end{cvitems}
   }	  
\end{cventries}
