\cvsection{Relevant Academic Publications}

\vspace{-5.5mm}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Degree
    {} % Institution
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {{\bf Semi-Supervised Bootstrapping of Relationship Extractors with Distributional Semantics}. David S Batista, Bruno Martins, and Mário J Silva. In {\it In Empirical Methods in Natural Language Processing-EMNLP'15} - {\bf Honorable Mention for Best Short Paper}}
		\vspace{2.0mm}
		\item {{\bf A Minwise Hashing Method for Addressing Relationship Extraction from Text}. David S Batista, Rui Silva, Bruno Martins, and Mário J Silva. In {\it Web Information Systems Engineering-WISE'13}}
		\vspace{2.0mm}
		\item {{\bf Exploring DBpedia and Wikipedia for Portuguese Semantic Relationship Extraction} David Soares Batista, David Forte, Rui Silva, Bruno Martins, and Mário J. Silva. {\it Linguamática,} 5(1), 2013}
		\vspace{2.0mm}
		\item {{\bf Toponym Disambiguation using Ontology-based Semantic Similarity} David S Batista, João D Ferreira, Francisco M Couto, and Mário J Silva. In {\it Computational Processing of the Portuguese Language 2012}}
		\vspace{2.0mm}
		\item {{\bf POWER - Politics Ontology for Web Entity Retrieval} Silvio Moreira, David Batista, Paula Carvalho, Francisco M Couto, and Mário J Silva. In {\it Advanced Information Systems Engineering Workshops. Springer, 2011}}
		\vspace{2.0mm}
		\item {{\bf A Statistical Study of the WPT05 Crawl of the Portuguese Web} David Batista and Mário J Silva. In {\it FALA 2010 VI Jornadas en Tecnología del Habla and II Iberian SLTech Workshop, Vigo, Spain}}
		\vspace{2.0mm}
		\item {{\bf Geographic Signatures for Semantic Retrieval} David S Batista, Mário J Silva, Francisco M Couto, and Bibek Behera. In {\it Proceedings of the 6th Workshop on Geographic Information Retrieval} ACM, 2010.}		
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}



\begin{comment}
\begin{cventries}

\cventry
    {X} % Degree
    {X} % Institution
    {X} % Location
    {X} % Date(s)
	{
		\begin{cvitems}

			\item {\textbf{}. . \textit{}. - \textbf{}}






	\end{cvitems}
	}
\end{cventries}
\end{comment}